A performance assessment of evolutionary algorithms in a volunteer computing system

### 2016-03-20 PPSN2016/paper.Rnw
Back to 10 pages

\begin{table}[htb]
\caption{Experiment table, with summary of results. \label{tab:runs}}
\begin{center}
\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
\hline
Experiment & Median Time & \multicolumn{2}{|c|}{Median IPs} &
\multicolumn{3}{|c|}{Median PUTs} & \#Runs & Unique IPs & Puts/IP \\
           &   (ms)        & Total & Used & Total & Used & Ratio &  & & \\
\hline
base & 120056.0 & 10 & 4 & 256.0 & 21.0 & 0.1290323 & 81 & 262 & 21.33333\\
\hline
graph1 & 152619.5 & 9 & 4 & 212.5 & 26.5 & 0.1282238 & 36 & 96 & 24.30000\\

@@

%
%
\begin{figure}[htbp]
\centering
<<zipf, cache=FALSE,echo=FALSE,fig.height=3>>=
ggplot(ips.data,aes(x=idx,y=PUTs,group=Experiment,color=Experiment))+geom_point()+scale_y_log10()+ scale_colour_discrete(labels=c('base','graph1','graph2','reboot','cachereboot'))+scale_x_log10()
@ %def graph for IPs and puts
%
\caption{Ranked and normalized number of contributions (PUTs) per IP,
  plotted in a log $y$ scale.\label{fig:zipf}}
\end{figure}
%
Every run had slightly different conditions, although in some cases it
was just a server reboot and a new round of announcements. Each run
batch included at least 30 completions, that is, evolution until the
solution was found. The number of runs was controlled by polling an
URL that indicated the number of runs made in the present batch so
far. Every volunteer contributed a certain number of individuals
(represented by the PUT HTTP request) to the server. The ranked number
of contributions per unique IP is shown in Figure \ref{fig:zipf} in a
log-log scale. Besides following the usual Zipf's law found in our
previous work and thus having a very similar appearance for all 5 sets, it
is interesting to see how some sets have a number of contributions per
IP that are slightly superior to the rest, specially so in {\tt
  graph2}. The last two sets, {\tt reboot} and {\tt cachereboot}, also
show a regime in the middle of the graph that shows that some users
are contributing more than in other similar sets. In general, these
differences in behavior are due more to the specific users that show
up in these experiments than to general laws, but it should also be
noted that those behaviors can be encouraged by design.

@@

\begin{table}[htbp]
  \caption{Minute-wise correlation for number of participating volunteers. \label{tab:correlation}}
\begin{center}
<<correlations, cache=FALSE,echo=FALSE>>=
ip.correlations$Experiment <- c("base","graph1","reboot","cachereboot")
kable(ip.correlations)
@ %def correlations
\end{center}
\end{table}
%
We can check this impact by looking at the column that refers to
median time in Table \ref{tab:filtered} and its relation to the median
number of PUTs, which reflects the number of evaluations performed by
the clients. The two last rows have a low number of evaluations,
around 650, which is higher than the first two, probably due to the
lower volunteer supply, but better than the middle one; besides, the
amount is remarkably similar. But in the last case, it takes much less
time to find the solution {\em using the same number of
  evaluations}. All variables are difficult to control in this
environment, but it might be due to the fact that parallelism has
increased, there are more volunteers contributing at the same time. In
fact, as it can be seen in the last column, the median number of
contributions per user is {\em much lower} in the last row, which
indicates that {\tt cachereboot} needs less contributions by users to
find the same solution. Besides, the last row shows that {\em all}
users actively contribute to the cache, while in the {\tt reboot}
strategy 30\% of users do not. This might be due to the fact that {\tt
  reboot} only does so when cache size is less than one. With very
fast clients there might be some clients that do not detect that
change and might, in fact, continue with their former run, thus not
contributing to the current common cache.

>>>>

\begin{table}[htb]
\caption{Summary of results for the 5 sets of experiments.\label{tab:runs}}
\begin{center}
\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
\hline
Experiment & Median Time & \multicolumn{2}{|c|}{Median IPs} &
\multicolumn{3}{|c|}{Median PUTs} & \#Runs & Unique IPs & Puts/IP \\
           &   (ms)        & Total & Used & Total & Used & Ratio &  & & \\
\hline
base & 120056.0 & 10 & 4 & 256.0 & 21.0 & 0.1290323 & 81 & 262 & 21.33333\\
\hline
graph1 & 152619.5 & 9 & 4 & 212.5 & 26.5 & 0.1282238 & 36 & 96 & 24.30000\\

@@

%
%
\begin{figure}[htbp]
\centering
<<zipf, cache=FALSE,echo=FALSE,fig.height=3>>=
ggplot(ips.data,aes(x=idx,y=PUTs,group=Experiment,color=Experiment))+geom_point()+scale_y_log10()+ scale_colour_discrete(labels=c('base','graph1','graph2','reboot','cachereboot'))+scale_x_log10()
@ %def graph for IPs and puts
%
\caption{Log-log plot of ranked and normalized number of contributions (PUTs) per IP.\label{fig:zipf}}
\end{figure}
%
Every run had slightly different conditions, although in some cases it
was just a server reboot and a new round of announcements. Each run
batch included at least 30 completions, that is, evolution until the
solution was found. The number of runs was controlled by polling an
URL that indicated the number of runs made in the present batch so
far. Every volunteer contributed a certain number of individuals
(represented by the PUT HTTP request) to the server. The ranked number
of contributions per unique IP is shown in Figure \ref{fig:zipf} in a
log-log scale. Besides following the usual Zipf's law found in our
previous work and thus having a very similar appearance for all 5 sets, it
is interesting to see how some sets have a number of contributions per
IP that are slightly superior to the rest, specially so in {\tt
  graph2}. The last two sets, {\tt reboot} and {\tt cachereboot}, also
show a regime in the middle of the graph that shows that some users
are contributing more than in other similar sets. In general, these
differences in behavior are due more to the specific users that show
up in these experiments than to general laws, but it should also be
noted that those behaviors can be encouraged by design.

@@

\begin{table}[htbp]
  \caption{Minute-wise correlation for number of participating volunteers. \label{tab:correlation}}
\begin{center}
<<correlations, cache=FALSE,echo=FALSE>>=
ip.correlations$Experiment <- c("base","graph1","reboot","cachereboot")
kable(ip.correlations)
@ %def correlations
\end{center}
\end{table}
%
We can check this impact by looking at the column that refers to
median time in Table \ref{tab:filtered} and its relation to the median
number of PUTs, which reflects the number of evaluations performed by
the clients. The two last rows have a low number of evaluations,
around 650, which is higher than the first two, probably due to the
lower volunteer supply, but better than the middle one; besides, the
amount is remarkably similar. But in the last case, it takes much less
time to find the solution {\em using the same number of
  evaluations}. All variables are difficult to control in this
environment, but it might be due to the fact that parallelism has
increased, there are more volunteers contributing at the same time. In
fact, as it can be seen in the last column, the median number of
contributions per user is the lowest for {\tt cachereboot}, which so needs less contributions by users to
find the same solution. Besides, the last row shows that {\em all}
users actively contribute to the cache, while in the {\tt reboot}
strategy 30\% of users do not. This might be due to the fact that {\tt
  reboot} only does so when cache size is less than one, indicating
that this strategy is only partly successful in avoiding overlaps.
